Main Figures

### 2020-10-30 figure_manuscript/codes_of_figures.Rmd
figure code update

pa1 <- ggVennDiagram(x_gene, label = "count", category.names = c("Tumor","Normal"))+
  scale_fill_gradient(low='bisque1',high = 'lightsalmon')+
  theme(legend.position="none", text = element_text(""), plot.margin = margin(0, 0, 0, 0, "mm"))

@@

@@

pa2
```
## Functional Annotation Analysis

>>>>

pa1 <- ggVennDiagram(x_gene, label = "both", category.names = c("Tumor","Normal"))+
  scale_fill_gradient(low='bisque1',high = 'lightsalmon')+
  theme(legend.position="none", text = element_text(""), plot.margin = margin(0, 0, 0, 0, "mm"))

@@

ggsave(filename = 'lim1_PE_gene_mirtarbase.eps', device=cairo_ps, width = 6, height = 3)

@@

pa2
```

```{r, eval=FALSE}
library(ggpubr)

#pA <- grid.arrange(pa1, pa2)

pA <- ggpubr::ggarrange(pa1, pa2, nrow = 2)
pA
#ggsave(filename = 'lim1_PE_gene_mirtarbase.svg', width = 6, height = 6)
```

## Functional Annotation Analysis
